Are shade leaves lying in wait? How instantaneous responses of mesophyll conductance to light availability in shade leaves impacts canopy carbon gain

### 2015-07-14 manuscript/manuscript_wtc3.Rmd
added data table for resouces
started 2 data tables in manuscrupts

---
title: "Are shade leaves lying in wait? How instantaneous responses of mesophyll conductance to light availability in shade leaves affect theories of optimal canopy carbon gain"
author: ""
date: ""
output:
  word_document:
    reference_docx: manuscriptstyle.docx
  pdf_document: default
  html_document:
    number_sections: yes
csl: new-phytologist.csl
bibliography: references.bib
---

@@

@@

>>>>

---
title: "Are shade leaves lying in wait? How instantaneous responses of mesophyll conductance to light availability in shade leaves impacts canopy carbon gain"
author: ""
date: ""
output:
  word_document:
    reference_docx: manuscriptstyle.docx
  pdf_document: default
  html_document:
    number_sections: yes
csl: new-phytologist.csl
bibliography: references.bib
---

@@

* overview
* method
* big result
* implication

@@

# Tables {.unnumbered}

```{r tablex, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
library(ascii)
resource_table <- read.csv("master_scripts/resource_table.csv")
print(ascii(resource_table,  include.rownames=FALSE,
          colnames =c("Leaf", "Temperature", "LMA", "Narea", "Vcmax", "Jmax", 
                       "Leaf K", "WP_pre", "WP_mid", "13C")),type="pandoc")

```
**Table 1.** Canopy resouce distribution among sun and shade leaves under elevated and ambient termperatures

```{r table1, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
library(ascii)
phystable <- read.csv("master_scripts/ge_table.csv")
print(ascii(phystable,
            include.rownames=FALSE,
            colnames=c("Leaf", "Temperature", "Light", "Photosynthesis", "gs", "gm", 
                       "Ci", "Transpiration", "VPD")),
            type='pandoc')

```
**Table 2.** Mean gas exchange parameters across leaf types with light and temperature treatments
